Fast and robust ancestry inference using principal component analysis

### 2018-06-21 doc/paper/paper.tex
Correct typos in paper

 Population stratification (PS) is a major confounder in genome-wide association studies (GWAS) and can lead to false positive associations. To adjust for PS, principal component analysis (PCA)-based ancestry prediction has been widely used. This approach first performs PCA on the reference samples with detailed ancestry information and then uses the reference sample PCA results to predict the PC scores of the study samples. Simple Projection (SP) and Augmentation-Decomposition-Transformation (ADP), such as LASER and TRACE, are popular methods for predicting PC scores. However, they are either biased or computationally expensive. For example, the predicted PC scores from SP can be biased toward NULL. On the other hand, since ADP requires running PCA separately for each study sample on the augmented dataset, its computational cost is high.

To address these problems, we propose two alternative approaches, Adjusted Projection (AP) and Online ADP (OADP), implemented in the genoPCA software. Using random matrix theory results, AP asymptotically estimates and adjusts for the bias of SP. Moreover, OADP uses online singular value decomposition, which can greatly reduce the computation cost of ADP. We carried out extensive simulation studies to show that these alternative approaches are unbiased and that the computation times are 10-100 times faster than ADP when 2000 reference samples are used. We also applied our approaches to 500,000 study samples from the UK biobank data with 2,500 samples from the 1000 Genomes data as the reference. AP and OADP required 16 and 90 CPU hours, respectively, while the projected computation time of ADP is 1,828 CPU hours. Furthermore, when we only used the European reference samples in the 1000 Genomes to infer sub-European ancestry, SP clearly showed bias, unlike the proposed approaches. By using AP and OADP, we can infer ancestry and adjust for PS in GWAS robustly and efficiently

@@

Population stratification (PS) is an important confounder for the association between
genotypes and phenotypes \citep{price2006principal}.
To adjust for PS, we need to accurately estimate the ancestry structure in the study samples.
Principle component analysis (PCA) is a multivariate statistical method
which finds the direction of the maximum variability among the samples.
By aggregating information across all genetic markers,
PCA can accurately infer the ancestry structure \citep{reich2008principal}.
To adjust for PS,
PCA can be applied to study data to calculate the principle component (PC) scores,
which are regarded as variables of ancestry direction
and can be used as covariates to adjust for.
An alternative approach for doing PCA is
predicting the PC scores of the study samples
by using some reference genotyped samples with detailed ancestry information.
This prediction-based approach allows not only adjustment for PS
but also infererence of the ancestry memberships of the study samples.

@@

\begin{enumerate}
\item Compute the reference covariance matrix $X^T X$.
  (Computational complexity (CC): $\bO[pn^2]$.)  
\item EGD on the reference covariance matrix: $X^T X = V D^2 V^T$.
  (CC: $\bO[n^3]$.)
\item Compute the PC loading matrix for the top $k$ PCs only: $U_k= X V_k D_k^{-1}$.
Here $V_k$ and $D_k$
are the the first $k$ columns of $V$
and the upper-left $k \times k$ submatrix of $D$, respectively.
(CC: $\bO[pnk]$.)
\item Compute the predicted study PC scores for the top $k$ PCs: $W_k = Y^T U_k$.
(CC: $\bO[mpk]$.)
\end{enumerate}
The total computational complexity is  $\bO[pn^2 + mpk]$
given that $k \ll n \ll p$.
The computational complexity for each study sample is $\bO[pk]$,
which is the lowest among all the methods discussed in this paper.
However, though computationally efficient,
a major disadvantae of SP is the loss of accuracy when the number of features $p$ greatly exceeds the reference sample size $n$,
a situation that is not uncommon for genotype data.
\citet{dey2016asymptotic} have shown that when $n \ll p$,
especially when the signals in the reference samples are not strong,
the predicted PC scores will shrink toward the origin.
This shrinkage bias limits the accuracy of SP for high dimensional data.
Fortunately, \citet{dey2016asymptotic} have also provided a way
to estimate the asymptotic shrinkage magnitude and angle
and implemented it in the \verb|hdpca| package in the R language \citep{hdpca}.
We use this estimation to eliminate the shrinkage bias,
as in the AP method.

@@

\begin{enumerate}
\item Compute the reference covariance matrix $X^T X$.
  (CC: $\bO[pn^2]$.)  
\item EGD on the reference covariance matrix: $X^T X = V D^2 V^T$.
  (CC: $\bO[n^3]$.)
\item Estimate the shrinkage magnitudes and organize them in a $n \times n$ diagonal matrix $S$.
  (CC: $\bO[p]$.)
\item Compute the PC loading matrix for the top $k$ PCs with the adjustment for the shrinkage bias: $U_k= X V_k D_k^{-1} S_k^{-1}$.
Here $V_k$, $D_k$, and $S_k$
are the the first $k$ columns of $V$
and the upper-left $k \times k$ submatrices $D$ and $S$, respectively.
(CC: $\bO[pnk]$.)
\item Compute the predicted study PC scores for the top $k$ PCs: $W_k = Y^T U_k$.
(CC: $\bO[mpk]$.)
\end{enumerate}
Given that $k \ll n \ll p$,
the total computational complexity is $\bO[pn^2 + mpk]$,
which is the same as that of SP.
Thus the adjustment for the shrinkage bias in AP
does not increase the computational complexity of SP
(though it does slightly increase the empirical runtimes).
A minor disadvantage of AP is that
while the computatinal complexity and memory usage of SP
can be further reduced
by using some truncated SVD algorithm
(such as the randomized SVD algorithm
by \citet{halko2011finding}
as discussed in \cref{sec:randsvd})
to compute the SVD for only the top $k$ PCs of the reference matrix,
AP requires all the eigenvalues
and thus a full SVD or EGD of the reference matrix.

@@

\begin{enumerate}
\item Compute the reference covariance matrix $X^T X$.
  (CC: $\bO[pn^2]$.)  
\item Apply EGD to the reference corariance matrix
  to obtain $X^T X = V D^2 V^T$.
  (CC: $\bO[n^3]$.)
\item For a study sample $y$,
  find the augmented covariance matrix
  $\tilde{X}^T \tilde{X}$
  by computing $X^T y$, $(X^T y)^T$, and $y^T y$
  and appending them to the
  bottom edge,
  right edge,
  and bottom-right corner of $X^TX$.
  (CC: $\bO[pn]$.)
\item Apply EGD to $\tilde{X}^T \tilde{X}$ to get $\tilde{X}^T \tilde{X} = \tilde{V} \tilde{D}^2 \tilde{V}^T$.
  (CC: $\bO[n^3]$.)
\item Find the Procrutes transformation
from the first $lk$ columns of $\tilde{V}$
to the first $k$ columns of $V$.
  (CC: $\bO[nk^2]$)
  \item Go to step 3 for the next study sample
  until all the study samples are analyzed.
\end{enumerate}
The total computational complexity is
$\bO[pn^2 + m(np + n^3)]$
given that $lk \ll n \ll p$.

ADP is regarded as the most accurate method for predicting study PC scores \todo{Find citation}.
It does not have SP's shrinkage bias.
However, the major disadvantage of ADP
is its high computational complexity.
In particular,
as the reference size increases,
the computational cost for a study sample
increases cubically.
Fortunately, this disadvantage can be mitigated by taking some computational shortcuts,
as in the OADP method.

@@

\begin{enumerate}
\item Compute $X^T X$.
  (Computational complexity: $\bO[n^2p]$.)  
\item Apply eigendecomposition to $X^T X$ to get $X^T X = V D^2 V^T$,
  where $D$ and $V$ only need their first $k$ columns.
  ($\bO[n^3]$.)
\item Calculate $U = X V D^{-1}$ but for the first $k$ columns only.
  ($\bO[k n p]$.)
\item Calculate 
  \[
    L = U^T y \quad \text{and} \quad K = y^T H,
  \]
  where $H$ is the normalized  $y - UL$
  ($\bO[k p]$.)
\item Calculate $Q^T Q$, where
  \[
    Q = 
    \begin{bmatrix}
      D & L \\
      0 & K
    \end{bmatrix}.
  \]
  ($\bO[k^3]$.)
\item Apply eigendecomosition to $Q^T Q$ to get $Q^T Q = \ddot{V} \ddot{D}^2 \ddot{V}^T$.
  ($\bO[k^3]$.)
\item Calculate
  \[
    \tilde{V} =
    \begin{bmatrix}
      V & 0 \\
      0 & 1
    \end{bmatrix}
    \ddot{V}.
  \]
  ($\bO[nk^2]$.)
\item Transform the first $k_2$ columns of $\tilde{V}$ to the first $k_1$ columns of $V$ by using Procrustes analysis to get the transformed PC scores of the study individual,
  where $k_1 < k_2  < k \ll n$.
  (Computational complexity is negligible if $k_2$ is small compared to $n$.)
  \item Go to step 4 for the next study individual.
\end{enumerate}

@@

For AP and OADP, their predicted PC1 and PC2 scores
for the European study samples
were almost identical
to those done by ADP.
The three methods' classification
agreed on most of the samples,
except for within the cluster of CEU and GBR.
Since many residents with northern and western European ancestry living in Utah
could originally migrated from Britain,
these two groups' ancestral history could be very similar
and thus difficult if not impossible to be separated by PCA.
Hence any slightest change
in the PC scores for these two groups' study samples
could easily change the classification from one group to the other.
This is a problem inherent to the population structure
and is not caused by the limitations of our methods.
The patterns discussed above
were still observed
when we used all the 488,000 study samples in the UK Biobank dataset
and those predicted to be Europeans among them (\Cref{fig:ukb,fig:ukb_eur}).

@@

For the future, we would like
to improve the parallelism of our genoPCA software.
We are also interested in applying randomized SVD algorithms
such as the one by \citet{halko2011finding}
for PCA on the reference data,
since as the reference sample size becomes larger and larger,
it becomes impractical to load such a large matrix into memory
to compute its SVD or ED.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim_runtimes.png}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim_errors_adp.png}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim_errors_ctr.png}
  \caption{
    The runtimes and errors of the four methods
    as the reference size increases.
    Runtimes are measured in seconds.
    Errors from ADP are the Euclidean distance
    from each method's result to ADP's result.
    Errors between centers are the Euclidean distance
    from the centers of mass of the reference populations
    to the corresponding centers of mass of the study populations.
    The number of variants is 100,000,
    and the study sample size is 200.
    Only the top 4 PCs are calculated.
    The data is simulated by the GGS software \citep{mathieson2012differential}.
    \label{fig:ggsim_trend}
  }
\end{figure}

@@

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_sp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_ap}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_oadp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_adp}
  \caption{PC scores of 500 randomly selected global samples in UK Biobank data (circles) predicted by the four methods with the global samples in the 1000 Genomes data (squares) as the reference.}
  \label{fig:ukb_500}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_sp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_ap}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_oadp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_adp}
  \caption{PC scores of the European in the 500 randomly selected global samples UK Biobank data (circles) predicted by the four methods with the European samples in the 1000 Genomes data (squares) as the reference.}
  \label{fig:ukb_500_eur}
\end{figure}

>>>>

 Population stratification (PS) is a major confounder in genome-wide association studies (GWAS) and can lead to false positive associations. To adjust for PS, principal component analysis (PCA)-based ancestry prediction has been widely used. This approach first performs PCA on the reference samples with detailed ancestry information and then uses the reference sample PCA results to predict the PC scores of the study samples. Simple Projection (SP) and Augmentation-Decomposition-Transformation (ADP), such as LASER and TRACE, are popular methods for predicting PC scores. However, they are either biased or computationally expensive. For example, the predicted PC scores from SP can be biased toward NULL. On the other hand, since ADP requires running PCA separately for each study sample on the augmented data set, its computational cost is high.

To address these problems, we propose two alternative approaches, Adjusted Projection (AP) and Online ADP (OADP), implemented in the genoPCA software. Using random matrix theory results, AP asymptotically estimates and adjusts for the bias of SP. Moreover, OADP uses online singular value decomposition, which can greatly reduce the computation cost of ADP. We carried out extensive simulation studies to show that these alternative approaches are unbiased and that the computation times are 10-100 times faster than ADP when 2000 reference samples are used. We also applied our approaches to 500,000 study samples from the UK Biobank data with 2,500 samples from the 1000 Genomes data as the reference. AP and OADP required 16 and 90 CPU hours, respectively, while the projected computation time of ADP is 1,828 CPU hours. Furthermore, when we only used the European reference samples in the 1000 Genomes to infer sub-European ancestry, SP clearly showed bias, unlike the proposed approaches. By using AP and OADP, we can infer ancestry and adjust for PS in GWAS robustly and efficiently

@@

Population stratification (PS) is an important confounder for the association between
genotypes and phenotypes \citep{price2006principal}.
To adjust for PS, we need to accurately estimate the ancestry structure in the study samples.
Principle component analysis (PCA) is a multivariate statistical method
which finds the direction of the maximum variability among the samples.
By aggregating information across all genetic markers,
PCA can accurately infer the ancestry structure \citep{reich2008principal}.
To adjust for PS,
PCA can be applied to study data to calculate the principle component (PC) scores,
which are regarded as variables of ancestry direction
and can be used as covariates to adjust for.
An alternative approach for doing PCA is
predicting the PC scores of the study samples
by using some reference genotyped samples with detailed ancestry information.
This prediction-based approach allows not only adjustment for PS
but also inference of the ancestry memberships of the study samples.

@@

\begin{enumerate}
\item Compute the reference covariance matrix $X^T X$.
  (Computational complexity (CC): $\bO[pn^2]$.)  
\item EGD on the reference covariance matrix: $X^T X = V D^2 V^T$.
  (CC: $\bO[n^3]$.)
\item Compute the PC loading matrix for the top $k$ PCs only: $U_k= X V_k D_k^{-1}$.
Here $V_k$ and $D_k$
are the the first $k$ columns of $V$
and the upper-left $k \times k$ submatrix of $D$, respectively.
(CC: $\bO[pnk]$.)
\item Compute the predicted study PC scores for the top $k$ PCs: $W_k = Y^T U_k$.
(CC: $\bO[mpk]$.)
\end{enumerate}
The total computational complexity is  $\bO[pn^2 + mpk]$
given that $k \ll n \ll p$.
The computational complexity for each study sample is $\bO[pk]$,
which is the lowest among all the methods discussed in this paper.
However, though computationally efficient,
a major disadvantage of SP is the loss of accuracy when the number of features $p$ greatly exceeds the reference sample size $n$,
a situation that is not uncommon for genotype data.
\citet{dey2016asymptotic} have shown that when $n \ll p$,
especially when the signals in the reference samples are not strong,
the predicted PC scores will shrink toward the origin.
This shrinkage bias limits the accuracy of SP for high dimensional data.
Fortunately, \citet{dey2016asymptotic} have also provided a way
to estimate the asymptotic shrinkage magnitude and angle
and implemented it in the \verb|hdpca| package in the R language \citep{hdpca}.
We use this estimation to eliminate the shrinkage bias,
as in the AP method.

@@

\begin{enumerate}
\item Compute the reference covariance matrix $X^T X$.
  (CC: $\bO[pn^2]$.)  
\item EGD on the reference covariance matrix: $X^T X = V D^2 V^T$.
  (CC: $\bO[n^3]$.)
\item Estimate the shrinkage magnitudes and organize them in a $n \times n$ diagonal matrix $S$.
  (CC: $\bO[p]$.)
\item Compute the PC loading matrix for the top $k$ PCs with the adjustment for the shrinkage bias: $U_k= X V_k D_k^{-1} S_k^{-1}$.
Here $V_k$, $D_k$, and $S_k$
are the the first $k$ columns of $V$
and the upper-left $k \times k$ submatrices $D$ and $S$, respectively.
(CC: $\bO[pnk]$.)
\item Compute the predicted study PC scores for the top $k$ PCs: $W_k = Y^T U_k$.
(CC: $\bO[mpk]$.)
\end{enumerate}
Given that $k \ll n \ll p$,
the total computational complexity is $\bO[pn^2 + mpk]$,
which is the same as that of SP.
Thus the adjustment for the shrinkage bias in AP
does not increase the computational complexity of SP
(though it does slightly increase the empirical runtimes).
A minor disadvantage of AP is that
while the computational complexity and memory usage of SP
can be further reduced
by using some truncated SVD algorithm
(such as the randomized SVD algorithm
by \citet{halko2011finding}
to compute the SVD for only the top $k$ PCs of the reference matrix,
AP requires all the eigenvalues
and thus a full SVD or EGD of the reference matrix.

@@

\begin{enumerate}
\item Compute the reference covariance matrix $X^T X$.
  (CC: $\bO[pn^2]$.)  
\item Apply EGD to the reference corariance matrix
  to obtain $X^T X = V D^2 V^T$.
  (CC: $\bO[n^3]$.)
\item For a study sample $y$,
  find the augmented covariance matrix
  $\tilde{X}^T \tilde{X}$
  by computing $X^T y$, $(X^T y)^T$, and $y^T y$
  and appending them to the
  bottom edge,
  right edge,
  and bottom-right corner of $X^TX$.
  (CC: $\bO[pn]$.)
\item Apply EGD to $\tilde{X}^T \tilde{X}$ to get $\tilde{X}^T \tilde{X} = \tilde{V} \tilde{D}^2 \tilde{V}^T$.
  (CC: $\bO[n^3]$.)
\item Find the Procrustes transformation
from the first $lk$ columns of $\tilde{V}$
to the first $k$ columns of $V$.
  (CC: $\bO[nk^2]$)
  \item Go to step 3 for the next study sample
  until all the study samples are analyzed.
\end{enumerate}
The total computational complexity is
$\bO[pn^2 + m(np + n^3)]$
given that $lk \ll n \ll p$.

ADP is regarded as the most accurate method for predicting study PC scores \todo{Find citation}.
It does not have SP's shrinkage bias.
However, the major disadvantage of ADP
is its high computational complexity.
In particular,
as the reference size increases,
the computational cost for a study sample
increases cubicly.
Fortunately, this disadvantage can be mitigated by taking some computational shortcuts,
as in the OADP method.

@@

\begin{enumerate}
\item Compute $X^T X$.
  (Computational complexity: $\bO[n^2p]$.)  
\item Apply EGD to $X^T X$ to get $X^T X = V D^2 V^T$,
  where $D$ and $V$ only need their first $k$ columns.
  ($\bO[n^3]$.)
\item Calculate $U = X V D^{-1}$ but for the first $k$ columns only.
  ($\bO[k n p]$.)
\item Calculate 
  \[
    L = U^T y \quad \text{and} \quad K = y^T H,
  \]
  where $H$ is the normalized  $y - UL$
  ($\bO[k p]$.)
\item Calculate $Q^T Q$, where
  \[
    Q = 
    \begin{bmatrix}
      D & L \\
      0 & K
    \end{bmatrix}.
  \]
  ($\bO[k^3]$.)
\item Apply EGD to $Q^T Q$ to get $Q^T Q = \ddot{V} \ddot{D}^2 \ddot{V}^T$.
  ($\bO[k^3]$.)
\item Calculate
  \[
    \tilde{V} =
    \begin{bmatrix}
      V & 0 \\
      0 & 1
    \end{bmatrix}
    \ddot{V}.
  \]
  ($\bO[nk^2]$.)
\item Transform the first $k_2$ columns of $\tilde{V}$ to the first $k_1$ columns of $V$ by using Procrustes analysis to get the transformed PC scores of the study individual,
  where $k_1 < k_2  < k \ll n$.
  (Computational complexity is negligible if $k_2$ is small compared to $n$.)
  \item Go to step 4 for the next study individual.
\end{enumerate}

@@

For AP and OADP, their predicted PC1 and PC2 scores
for the European study samples
were almost identical
to those done by ADP.
The three methods' classification
agreed on most of the samples,
except for within the cluster of CEU and GBR.
Since many residents with northern and western European ancestry living in Utah
could originally migrated from Britain,
these two groups' ancestral history could be very similar
and thus difficult if not impossible to be separated by PCA.
Hence any slightest change
in the PC scores for these two groups' study samples
could easily change the classification from one group to the other.
This is a problem inherent to the population structure
and is not caused by the limitations of our methods.
The patterns discussed above
were still observed
when we used all the 488,000 study samples in the UK Biobank data set
and those predicted to be Europeans among them (\Cref{fig:ukb,fig:ukb_eur}).

@@

For the future, we would like
to improve the parallelism of our genoPCA software.
We are also interested in applying randomized SVD algorithms
such as the one by \citet{halko2011finding}
for PCA on the reference data,
since as the reference sample size becomes larger and larger,
it becomes impractical to load such a large matrix into memory
to compute its SVD or EGD.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=.90\linewidth]{img/ggsim_runtimes.png}
  \centering
  \includegraphics[width=.90\linewidth]{img/ggsim_errors_adp.png}
  \centering
  \includegraphics[width=.90\linewidth]{img/ggsim_errors_ctr.png}
  \caption{
    The runtimes and errors of the four methods
    as the reference size increases.
    Runtimes are measured in seconds.
    Errors from ADP are the Euclidean distance
    from each method's result to ADP's result.
    Errors between centers are the Euclidean distance
    from the centers of mass of the reference populations
    to the corresponding centers of mass of the study populations.
    The number of variants is 100,000,
    and the study sample size is 200.
    Only the top 4 PCs are calculated.
    The data is simulated by the GGS software \citep{mathieson2012differential}.
    \label{fig:ggsim_trend}
  }
\end{figure}

@@

\begin{figure}[p]
  \centering
  \includegraphics[width=0.90\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_sp}
  \includegraphics[width=0.90\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_ap}
  \includegraphics[width=0.90\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_oadp}
  \includegraphics[width=0.90\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_adp}
  \caption{PC scores of 500 randomly selected global samples in UK Biobank data (circles) predicted by the four methods with the global samples in the 1000 Genomes data (squares) as the reference.}
  \label{fig:ukb_500}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.9\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_sp}
  \includegraphics[width=0.9\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_ap}
  \includegraphics[width=0.9\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_oadp}
  \includegraphics[width=0.9\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_adp}
  \caption{PC scores of the European in the 500 randomly selected global samples UK Biobank data (circles) predicted by the four methods with the European samples in the 1000 Genomes data (squares) as the reference.}
  \label{fig:ukb_500_eur}
\end{figure}
